FlowFPX: Nimble Tools for Debugging Floating-Point Exceptions

### 2024-07-26 paper.tex
Clarify relation between GPU-FPX and FloatTracker (no formal one)

>>>>

\FT{} and \GPUFPX{} have no formal connection---that is, one does not
need to use \GPUFPX{} with \FT{}, nor vice-versa.
These two tools compliment one another in debugging mixed-paradigm
workloads, but they can be used in isolation.
\GPUFPX{} is a library exclusively for NVIDIA CUDA code and has no
special relation to Julia.
Nevertheless, in cases where Julia code leverages a CUDA kernel,
\GPUFPX and \FT{} can both aid in tracking down exceptional \fp{}
values.
